\large Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-13 Dissertation/Defense/defense.tex
videos full size

\begin{frame}
	\frametitle{2D Autonomous Exploration: Intel Research Lab}
	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=IRL.mp4,
  		flashvars={source=IRL.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

\begin{frame}
	\frametitle{3D Autonomous Exploration: Mars}
	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=Topological Mars Mapping and Autonomous Exploration in 3D.mp4,
  		flashvars={source=Topological Mars Mapping and Autonomous Exploration in 3D.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

@@

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=NRL_ground_test.mp4,
  		flashvars={source=NRL_ground_test.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=NRL_3D_large_space.mp4,
  		flashvars={source=NRL_3D_large_space.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=explore3D_SEH.mp4,
  		flashvars={source=explore3D_SEH.mp4}
		]{}{VPlayer.swf}
		}

@@

\begin{frame}
\frametitle{Future Directions}
	\begin{itemize}
		\item Localization: use probabilistic map and other onboard sensors to localize, thereby completing the SLAM problem with the novel mapping approach
		\item Computational improvements: determine collision-free costs more efficiently than Dijkstra's cost map
		\item Decentralize the algorithms so processes may be distributed among multiple agents
	\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Thanks}
\begin{itemize}
        	\item Special thanks to the US Naval Research Lab for support under project ``Intelligent Microflyer''
	\item Questions
\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{2D Autonomous Exploration: Intel Research Lab}
	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=IRL.mp4,
  		flashvars={source=IRL.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

\begin{frame}
	\frametitle{3D Autonomous Exploration: Mars}
	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=Topological Mars Mapping and Autonomous Exploration in 3D.mp4,
  		flashvars={source=Topological Mars Mapping and Autonomous Exploration in 3D.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

@@

	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
    		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=NRL_ground_test.mp4,
  		flashvars={source=NRL_ground_test.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=NRL_3D_large_space.mp4,
  		flashvars={source=NRL_3D_large_space.mp4}
		]{}{VPlayer.swf}
		}

@@

	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=explore3D_SEH.mp4,
  		flashvars={source=explore3D_SEH.mp4}
		]{}{VPlayer.swf}
		}

@@

\begin{frame}
\frametitle{Future Directions}
	\begin{itemize}
		\item Localization: use probabilistic map and other onboard sensors to localize, thereby completing the SLAM problem with the novel mapping approach
		\item Computational improvements: determine collision-free costs more efficiently than Dijkstra's cost map
		\item Decentralize the algorithms so processes may be distributed among multiple agents
		\vspace*{0.3cm}
		\item Special thanks to the US Naval Research Lab for support under project ``Intelligent Microflyer''
	\end{itemize}
\end{frame}

@@
